---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aesmapr

<!-- badges: start -->
<!-- badges: end -->

`aesmapr` helps you create nice looking (decorative) maps of a local area. 

Due to data availability, it can currently be used for GB locations only. 

## Installation

You can install the development version of aesmapr from 
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("n-fanton/aesmapr")
```

## Example

The main function in `aesmapr` is `create_map()`, which allows you to vary the
location, shape, and extent of your outputs. 

```{r map_1, message=FALSE, warning=FALSE, dev='svg'}
library("aesmapr")

map_1 <- create_map(
  postcode = "PH33 6TQ",
  x_dist = 3000,
  y_dist = 2000
)

map_1
```

Maps can also draw circular areas, rather than rectangles:

```{r map_2, message=FALSE, warning=FALSE, dev='svg'}
map_2 <- create_map(
  postcode = "PH33 6TQ",
  shape = "circle",
  radius = 1500
)

map_2
```

I'll continue to add functionality to this package as I work more on it!

